---
title: "Virginia Department of Environmental Quality Biological Monitoring Program: Benthic Assessment Factsheet"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
always_allow_html: yes
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(DT)
library(RODBC)
library(dplyr)
library(ggplot2)
library(scales)

```

```{r read in data, message=FALSE}

# Read in data and functions


source('accessConnection.R')

#User enter data

UserStation<-"4ASRE022.30"
startyear<- 2008
endyear<- 2014



annualdata<-selectStation(UserStation, startyear, endyear)
StationQRY<-stationqry(UserStation)

#Habitat data manipulation
hab<-selecthabitatStation(UserStation, startyear, endyear)

totHab <- hab %>%
  group_by(StationID, CollDate ) %>%
  mutate(TotalHabitat = sum(HabValue))



```


**Regional Office:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `r unique(StationQRY$DEQREG)`

**River Basin:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `r unique(StationQRY$Basin)`

**Stream Name:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;`r unique(StationQRY$StreamName)`

**Location Information:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;`r unique(StationQRY$Location)`

**Station ID:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;`r unique(annualdata$StationID)`






#### Biological Assessments for the Last Two Years
```{r table, message=FALSE}
basicTable(annualdata)
```

#### VSCI Scores
```{r graph}

bugplot(annualdata)

```


**Are there any seasonal differences noted?**

Biologist Enters information



**Summary of any comments associated with assessments**

Biologist Enters information


**Any factors observed in watershed that may be affecting the benthic community?**

Biologist Enters information


**Have there been any recent changes in activity in the watershed that may have affected the more recent bioassessments.  Are these changes likely to affect the benthic community for a short or long term basis?**

Biologist Enters information



#### Total Habitat Scores

```{r habitat table}

HabitatDT(totHab)
```


**Final Assessment Rating:**

